Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-28 paper/ms.tex
Add a little something about Stackel Fudge in the disk
Small update to numbers in text

Other methods for computing actions are used in the literature. For example,
the St\"ackel Fudge method \citep{2016MNRAS.457.2107S} which uses the
St\"ackel potential to approximate the Galactic potential
\citep{1985MNRAS.216..273D,2012MNRAS.426.1324B} is commonly used
\citep{2018arXiv180503653T,2018MNRAS.481.4093S,2018arXiv180803278T}.

@@

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. For an error in
$z$ ({\em upper} panels), the 95\textsuperscript{th} minus
5\textsuperscript{th} percentiles are $2.2$ and $6.2 \actunit$ for $J_r$ and
$J_z$, respectively. These are fractional errors of $5.7\%$ and $85.7\%$,
respectively. The error induced in $L_z$ is negligible, as expected since
$L_z$ does not depend on the value of $z$. It is worth pointing out that a
$100\,\pc$ error in an orbit with $z_{\text{max}}=425\,\pc$ --- a $24\%$ error
--- induced an $85.7\%$ error in the computation of $J_z$.

\Gus{For an error in the $x$ component (or Solar radius)}, the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $x$, $y$,
and $z \actunit$ for $J_r$, $L_z$ and $J_z$, respectively. These are
fractional errors of $x\%$, $y\%$ and $z\%$, respectively.

>>>>

Other methods for computing actions are used in the literature. For example,
the St\"ackel Fudge method \citep{2016MNRAS.457.2107S} which uses the
St\"ackel potential to approximate the Galactic potential
\citep{1985MNRAS.216..273D,2012MNRAS.426.1324B} is commonly used
\citep{2018arXiv180503653T,2018MNRAS.481.4093S,2018arXiv180803278T}. For
applications in the disk, the St\"ackel Fudge method is of acceptable
accuracy, but since we also consider halo orbits in this work we choose to use
orbit integration throughout \citep{2016MNRAS.457.2107S}.

@@

Figure~\ref{fig:one_orbit_wrong_ref} shows that the erroneous observer would
infer significant time evolution in their computed actions. For an error in
$z$ ({\em upper} panels), the 95\textsuperscript{th} minus
5\textsuperscript{th} percentiles are $2.2$ and $6.2 \actunit$ for $J_r$ and
$J_z$, respectively. These are fractional errors of $5.7\%$ and $85.7\%$,
respectively. The error induced in $L_z$ is negligible, as expected since
$L_z$ does not depend on the value of $z$. It is worth pointing out that a
$100\,\pc$ error in an orbit with $z_{\text{max}}=850\,\pc$ --- a $12\%$ error
--- induced a $43\%$ error in the computation of $J_z$.

For an error in the $x$ component (or Solar radius), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $6.9$, $47$,
and $0.71 \actunit$ for $J_r$, $L_z$ and $J_z$, respectively. These are
fractional errors of $21\%$, $3.1\%$ and $3.1\%$, respectively.
